Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-04 analysis/paper/paper.Rmd
Add statement on journal instruction
use double quotes and linebreak for full stop

Journals can encourage authors to deposit their data and code by providing instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources.

@@

When making your science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
Deposit and annotate biological materials with an herbarium or other repository.
Provide a full description of all equipment used, *e.g.*, 'a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals.' This allows end-users to identify what was used and identify the methods used more accurately.
Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on your research.

>>>>

Journals can encourage authors to deposit their data and code by providing instruction for how to deposit the data and code in a repository and mint a DOI to accompany these resources.
While our analysis was unable to detect any differences in journals providing such instruction and journals that did not, the trend did indicate that journals that provided such instruction had better scores for data and code availability.

@@

When making your science more open and reproducible, methods, software used (this includes items such as R, Julia or Python packages that were directly used in the analysis or production of the paper, etc.) should be cited properly.
Deposit and annotate biological materials with an herbarium or other repository.
Provide a full description of all equipment used, *e.g.*, "a Spectrum Technologies Watchdog 2700 weather station was used to record wind speed, direction, rainfall, temperature and relative humidity at one-hour intervals".
This allows end-users to identify what was used and identify the methods used more accurately.
Just as importantly, this acknowledges the contributions of others whose works were instrumental in your research.
This also helps ensure that you as a researcher can reconstruct what you have done since you will have good notes and documentation and be able to identify if something changes, *e.g.*, a package version, what effect it had on your research.
